Calendar-based graphics for visualising people's daily schedules

### 2017-07-07 main.Rmd
added code examples

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "svglite"
)
read_chunk('src/main.R')
```

@@

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 installed sensors counting pedestrians every hour across downtown Melbourne until recently. The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. (FIGURE ?: weekday at multiple sensors) Figure (?) lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

@@

Calendar-based graphics turn out to be a useful tool in unfolding human-related activities in temporal context (cite). For example, @VanWijkCluster1999 developed a calendar view of heatmap to represent the number of employees in the work place over a year, where colours indicate different clusters derived from the days. It remarkably contrasts weekdays and weekends, highlights public holiday, and presents other known seasons like school vacations, all of which have influence over the turn-outs in the office. The calendar-based heatmap was implemented in a couple of R packages: \pkg{ggTimeSeries} [@R-ggTimeSeries] and \pkg{ggcal} [@R-ggcal]. However, these techniques are too constrained to colour-encoding graphics and day of week considered as the smallest time window. Time of day, which serves as one of the most important aspect in explaining variations arising from pedestrian sensor data, will be neglected through daily aggregation. Additionally if simply using colours encoded as quantities, it may becomes less perceivable of the actual variations or behaviours from the viewer's perspective.

@@

@@

@@

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 installed sensors counting pedestrians every hour across downtown Melbourne until recently. The dataset can shed lights into understanding people's daily schedules, or assisting administration and business planning. Figure \ref{fig:facet-time} lends itself to a number of issues that make exploratory data visualisation challenging in many temporal-context applications involving human behaviours:

@@

```{r time-series-plot, fig.cap = "Time series plot"}
```

```{r facet-time, fig.cap = "Time facet"}
```

Calendar-based graphics turn out to be a useful tool in unfolding human-related activities in temporal context (cite). For example, @VanWijkCluster1999 developed a calendar view of heatmap to represent the number of employees in the work place over a year, where colours indicate different clusters derived from the days. It remarkably contrasts weekdays and weekends, highlights public holiday, and presents other known seasons like school vacations, all of which have influence over the turn-outs in the office. The calendar-based heatmap was implemented in a couple of R packages: \pkg{ggTimeSeries} [@R-ggTimeSeries] and \pkg{ggcal} [@R-ggcal]. However, these techniques are too constrained to colour-encoding graphics and day of week as the smallest time scale. Time of day, which serves as one of the most important aspect in explaining variations arising from pedestrian sensor data, will be neglected through daily aggregation. Additionally if simply using colours encoded as quantities, it may becomes less perceivable of the actual variations or behaviours from the viewer's perspective.

@@

```{r flinders-2016, fig.height = 6.5}
```

@@

```{r flinders-free, fig.height = 6.5}
```

@@

```{r scatterplot, fig.height = 5}
```

```{r overlay, fig.height = 6.5}
```

```{r boxplot, fig.height = 6.5}
```

### 2017-07-07 main.tex
added code examples

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. There have been 43 installed sensors counting
pedestrians every hour across downtown Melbourne until recently. The
dataset can shed lights into understanding people's daily schedules, or
assisting administration and business planning. (FIGURE ?: weekday at
multiple sensors) Figure (?) lends itself to a number of issues that
make exploratory data visualisation challenging in many temporal-context
applications involving human behaviours:

@@

Calendar-based graphics turn out to be a useful tool in unfolding
human-related activities in temporal context (cite). For example,
\citet{VanWijkCluster1999} developed a calendar view of heatmap to
represent the number of employees in the work place over a year, where
colours indicate different clusters derived from the days. It remarkably
contrasts weekdays and weekends, highlights public holiday, and presents
other known seasons like school vacations, all of which have influence
over the turn-outs in the office. The calendar-based heatmap was
implemented in a couple of R packages: \pkg{ggTimeSeries}
\citep{R-ggTimeSeries} and \pkg{ggcal} \citep{R-ggcal}. However, these
techniques are too constrained to colour-encoding graphics and day of
week considered as the smallest time window. Time of day, which serves
as one of the most important aspect in explaining variations arising
from pedestrian sensor data, will be neglected through daily
aggregation. Additionally if simply using colours encoded as quantities,
it may becomes less perceivable of the actual variations or behaviours
from the viewer's perspective.

@@

@@

@@

>>>>

This work was originally motivated by studying foot traffic in the city
of Melbourne \citep{ped}. There have been 43 installed sensors counting
pedestrians every hour across downtown Melbourne until recently. The
dataset can shed lights into understanding people's daily schedules, or
assisting administration and business planning. Figure
\ref{fig:facet-time} lends itself to a number of issues that make
exploratory data visualisation challenging in many temporal-context
applications involving human behaviours:

@@

{\centering \includegraphics[width=\textwidth]{figure/time-series-plot-1}

\caption[Time series plot]{Time series plot}\label{fig:time-series-plot}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics[width=\textwidth]{figure/facet-time-1}

\caption[Time facet]{Time facet}\label{fig:facet-time}
\end{figure}
\end{CodeChunk}

Calendar-based graphics turn out to be a useful tool in unfolding
human-related activities in temporal context (cite). For example,
\citet{VanWijkCluster1999} developed a calendar view of heatmap to
represent the number of employees in the work place over a year, where
colours indicate different clusters derived from the days. It remarkably
contrasts weekdays and weekends, highlights public holiday, and presents
other known seasons like school vacations, all of which have influence
over the turn-outs in the office. The calendar-based heatmap was
implemented in a couple of R packages: \pkg{ggTimeSeries}
\citep{R-ggTimeSeries} and \pkg{ggcal} \citep{R-ggcal}. However, these
techniques are too constrained to colour-encoding graphics and day of
week as the smallest time scale. Time of day, which serves as one of the
most important aspect in explaining variations arising from pedestrian
sensor data, will be neglected through daily aggregation. Additionally
if simply using colours encoded as quantities, it may becomes less
perceivable of the actual variations or behaviours from the viewer's
perspective.

@@

\begin{CodeChunk}

\begin{center}\includegraphics[width=\textwidth]{figure/flinders-2016-1} \end{center}

\end{CodeChunk}

@@

\begin{CodeChunk}

\begin{center}\includegraphics[width=\textwidth]{figure/flinders-free-1} \end{center}

\end{CodeChunk}

@@

\begin{CodeChunk}

\begin{center}\includegraphics[width=\textwidth]{figure/scatterplot-1} \end{center}

\end{CodeChunk}

\begin{CodeChunk}

\begin{center}\includegraphics[width=\textwidth]{figure/overlay-1} \end{center}

\end{CodeChunk}

\begin{CodeChunk}

\begin{center}\includegraphics[width=\textwidth]{figure/boxplot-1} \end{center}

\end{CodeChunk}
